Make the full map of Tanzania

### 2022-02-24 docs/tanzania_full_map.Rmd
Update python scripts for full country

>>>>

#### Preparation

**[Launch AWS instance]** a few instance could be used for different needs.

  - `g3.8xlarge`, 2 GPU, 16G GPU memory, $0.684/hr for SPOT instance.
  - `g3.16xlarge`, 4 GPU, 32G GPU memory, $1.368/hr for SPOT instance.
  - `g4dn.8xlarge`, 1 GPU, 16G GPU memory, $0.6528/hr for SPOT instance.
  - `g4dn.12xlarge`, 4 GPU, 64G GPU memory, $1.1819/hr for SPOT instance.

**[Clean and organize directories]** pull branch `full_country` of `hrlcm` to the instance, and create relative folders for dataset.

**[Parse dataset from Dropbox]** run script `hrlcm/utils/parse_dataset.sh` to parse dataset into the instance.

The instance should be ready to run training for now.

#### Training

Multiple type of models will be trained:
- Using all bands and image standardization
- Using all bands without image standardization
- Using only NICFI bands with image standardization
- Using only NICFI bands without image standardization

Run models:

```
python hrlcm/fit_compose_lr.py --exp_name unet_clr_200epc --num_workers 32 --gpu_devices '0,1,2,3' --epochs 201
```

Evaluation:

```
python hrlcm/evaluate.py --args_path 'results/tanzania/unet_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/tanzania/unet_clr_200epc/checkpoints/final.pth' --data_dir 'results/tanzania' --out_dir 'results/tanzania/evaluation' --stats_dir 'results/tanzania/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/evaluation /Users/pinot/Dropbox/research/hrlcm/results/tanzania/unet_clr_200epc
```

Prediction

```
python hrlcm/predict.py --args_path 'results/tanzania/unet_clr_200epc/checkpoints/args.pkl' --checkpoint_file 'results/tanzania/unet_clr_200epc/checkpoints/final.pth' --fname_predict 'dl_catalog_predict.csv' --data_dir 'results/tanzania' --out_dir 'results/tanzania/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 32 --batch_size 32 --gpu_devices '0,1,2,3'

scp -r ubuntu@ec2-18-191-228-234.us-east-2.compute.amazonaws.com:~/hrlcm/results/prediction /Users/pinot/Dropbox/research/hrlcm/results/tanzania
```

#### Tensorboard

If download log file to local machine, then it is easy to check the training loss curves.

`tensorboard --logdir='./tensorboard_dirs' --port=16007`

Do the following steps to use the tensorboard on a remote server (reference: https://blog.yyliu.net/remote-tensorboard/):

1. You need to start SSH with transfer the remote server’s port to your local PC:

    (on your local PC) `ssh -L 16007:127.0.0.1:16007 username@server_ip`

2. Then you may start the tensorboard on the remote server with the specific port we want to transfer:

    (on the remote server) `tensorboard --logdir='./tensorboard_dirs' --port=16007`
